A demonstration of the \LaTeXe\ class file for \itshape{SAGE Publications}

### 2015-11-24 body/intro.tex
fixed template, introdone up 1.2 not included

Most multipedal locomotion focus on cyclic walking gaits \citep{Kajita03a}. But executing
this behaviour on cluttered environments is dangerous, if not impossible.
in an analysis of their participation to the darpa challenge, \citeauthor{atkensondarpa}
noted: ``Except for egress, no robots in the DRC Finals used
the  stair  railings  or  any  form  of  bracing.   Even  drunk  people  are  smart  enough  to  use  nearby  supports.
Full body locomotion (handholds,  bracing,  leaning against a wall or obstacles) should be easier than our
current high performance minimum contact locomotion approaches."

Indeed, the current approach to locomotion planning is to avoid obstacles as much as possible, instead of using them
to faciliate locomotion. The reason for this, as the authors state, is that ``More contacts make tasks
mechanically easier, but algorithmically more complicated for planning, and the transitions are difficult to
both plan and control[...].  We have seen very few robot planners that are  capable of  generating this  behavior."

The difficulty of addressing such a problem comes both in practice from the proximity to the obstacles (that tends to make the sampling of valid configuration tedious) and in theory from the foliation of the configuration space, where zero-measure manifolds intersect in a combinatorial manner \citep{simeon-manipulation-04}.

@@

Most of the papers that followed the work of \citeauthor{conf/iser/BretlRLKA04} have explored alternative formulations to handle the combinatorial issue. Two main directions have been explored. \textbf{On one hand, local optimization of both the root trajectory \Pa and the contact positions $\mathcal{P}_2$} has been used, to trade the combinatorial of the complete problem for a differential complexity, at the cost of local convergence. A complete example of the potential offered by such approaches is given by \cite{Mordatch:2012:DCB:2185520.2185539}, followed by a successful adaptation to a real robot \citep{mordatch2015}. To keep reasonable computation times, the method uses a simplified dynamic model for the avatar. Still, the computation time is far from interactive  (about 1 minute of computation for a sequence of 20 contacts). \cite{DBLP:conf/humanoids/DeitsT14} propose to solve contact planning globally as a mixed integer problem, but only cyclic, bipedal locomotion is considered. Aside from the computation cost, a major drawback of these optimization based approaches is thus that they only offer local convergence when applied to acyclic contact planning.

>>>>

Most multipedal locomotion systems focus on cyclic walking gaits \citep{Kajita03a}. But executing
this behaviour on cluttered environments is dangerous, if not impossible.
In an analysis of their participation to the darpa challenge, \citeauthor{atkensondarpa}
noted: ``Except for egress, no robots in the DRC Finals used
the  stair  railings  or  any  form  of  bracing.   Even  drunk  people  are  smart  enough  to  use  nearby  supports.
Full body locomotion (handholds,  bracing,  leaning against a wall or obstacles) should be easier than our
current high performance minimum contact locomotion approaches."

Indeed, the current approach to locomotion planning is to avoid obstacles as much as possible, instead of using them
to faciliate locomotion. The reason for this, as the authors state, is that ``More contacts make tasks
mechanically easier, but algorithmically more complicated for planning, and the transitions are difficult to
both plan and control[...].  We have seen very few robot planners that are  capable of  generating this  behavior."
The difficulty of addressing such a problem comes both in practice from the proximity to the obstacles (that tends to make the sampling of valid configuration tedious) and in theory from the foliation of the configuration space, where zero-measure manifolds intersect in a combinatorial manner \citep{simeon-manipulation-04}.

Previous contributions that embrace the combinatorial provide complete approaches, not applicable in practice because they require hours of computations \citep{conf/iser/BretlRLKA04}.
More recent successes use a local solution, resulting in more reasonnable performances (still far from real time), at the cost of dynamically inconsistent behaviors \citep{Mordatch:2012:DCB:2185520.2185539}.
Neither global or local methods presents satifying performances, because planning simultaneously the robot trajectory and the contacts that allow
its execution is too costly.

As suggested by \citeauthor{Bouyarmane2009}, we believe that these two tasks can be treated sequentially within a global planner, while preserving the completeness of the search.
We go further and claim that this can be done at a much smaller cost, provided that necessary and sufficient conditions for contact feasibility can be formulated for the robot trajectory.
This paper presents a geometrical representation of these conditions, and a concrete implementation of such a decoupled planner.
This implementation results from a trade-off between a necessary and a sufficient condition for feasibility, allowing us to find solutions extremely rapidly,
while preserving a success rate superior to TODO \% in the demonstrated scenarios.

In the remainder of this introduction, we discuss further the current state of the art. This allows us to then situate more precisely our contributions.

@@

Most of the papers that followed the work of \citeauthor{conf/iser/BretlRLKA04} have explored alternative formulations to handle the combinatorial issue. Two main directions have been explored. \textbf{On one hand, local optimization of both the root trajectory \Pa and the contact positions $\mathcal{P}_2$} has been used, to trade the combinatorial of the complete problem for a differential complexity, at the cost of local convergence. A complete example of the potential offered by such approaches was propose \citep{Mordatch:2012:DCB:2185520.2185539} and successfully applied to a real robot \citep{mordatch2015}. To keep reasonable computation times, the method uses a simplified dynamic model for the avatar. Still, the computation time is far from interactive  (about 1 minute of computation for a sequence of 20 contacts). \citeauthor{DBLP:conf/humanoids/DeitsT14} propose to solve contact planning globally as a mixed integer problem, but only cyclic, bipedal locomotion is considered. Aside from the computation cost, a major drawback of these optimization based approaches is thus that they only offer local convergence when applied to acyclic contact planning.
